\documentclass{subfiles}
\begin{document}
    Multiple alignment is somewhat a generalization of the pair-wise alignment;
        in fact what it does is align three or more sequences and give the best
        possible alignment. Here the use of the word best is misleading,
        as we are about to explain.

    Consider the following: can we use dynamic programming to compute the best alignment,
        as done in the case of two sequences? Assume we want to align three sequences.
        If we proceed as done for the Needleman-Wunsh algorithm, we must 
        consider the \(n^{3}\) matrix these form. Also, how shall we compute the scores?
    
    The acute reader might have seen how the problem is isomorphic to the problem
        of computing the best path in an n-dimension Manhattan Cube.

    Since the dimensions of the matrix increase with the number of sequences, 
        a dynamic programming based approach should be avoided, 
        as these require \bigO{n^k} time, with \(k\) the number of sequences.

    \begin{remark*}
        Despite the complexity, dynamic programming based algorithms exist,
        but are only used in the case of few sequences with a relatively short length.
    \end{remark*}

    Hence, unless extreme precision is needed, (e.g. medical analysis), heuristic 
        algorithms suffice our needs. We use the remainder of this section
        to discuss a couple of such algorithms.

    \subsection{The greedy approach}
    \subfile{../sub/3.1 - Thre greedy approach}
    \clearpage
\end{document}
