\documentclass{subfiles} 
\begin{document}
    Let's now focus our attention onto the source itself.
        In general, the alphabets they use may not be suitable for transmission for various reasons. 
        For this reason, an \emph{encoder} is used to convert the source alphabet into a new one, 
        which is more suitable for transmission.
        On the receiving side, a \emph{decoder} is used to convert back to the original alphabet.
        This process is called \emph{source encoding/decoding}.

    Formally, given a source \(S\) defined on some alphabet, 
        and \(X\) a new alphabet, called the \emph{input alphabet}, 
        we define a function \(C : S \to X\) that maps sequences of symbols of \(S\)
        to sequences of symbols in \(X\). 
        A sequence of symbols in \(X\) is called a \emph{codeword}.

    Before we consider any particular \emph{code},
        let us consider the general case. 
        Let \(C\) be a generic mapping from a source \(S\) to some new alphabet \(X\).
        Since we have imposed no conditions on \(C\), one may define it in such a way that two or more
        source symbols share the same codeword.
        It is easy to observe that, in doing so, the decoded message may not be correct or even unique.

   \begin{example*}
        Consider the following alphabet: \(\Sigma = \set{s_{1}, s_{2}, s_{3}, s_{4}}\).
            Assume the code \(C = \set{0, 11, 01, 11}\) was defined for \(\Sigma\).
            How should we decode the text 000111? There are two possible interpretations: 
            either as \(s_{1}s_{1}s_{3}s_{2}\) or as \(s_{1}s_{1}s_{3}s_{4}\).
            As noted above, the decoded message may not be unique. 
            Moreover, without additional context, there is no way to determine which interpretation is correct.
    \end{example*}

    From the above example, we can conclude that a ``good'' code must encode each 
    source symbol with a unique codeword. 
    We call such codes \emph{non-singular codes}.
  
    \subsubsection{\Gls{ud}}\label{Sec:1.2.1}
    \subfile{../subsub/1.2.1 - UD codes}

    \subsubsection{Sardinas-Patterson algorithm}
    \subfile{../subsub/1.2.2 - Sardina-Patterson}

    \subsubsection{Prefix codes}
    \subfile{../subsub/1.2.3 - Prefix codes}
\end{document}
