\documentclass{subfiles}
\begin{document}
    Hamming code, proposed by Richard W. Hamming, is one of the most used linear codes
        to this day. More precisely, Hamming proposed a family of codes all with their
        minimal distance set to three. It also turns out that this family of codes is 
        perfect.

    Before presenting the generalized Hamming code, we describe two of its most 
        used variants: the \([7, 4, 3]_{2}\) and the \([3, 1, 3]_{2}\) Hamming code.
    
    \paragraph*{\([7, 4, 3]_{2}\) Hamming code}
    The code is composed of \(16\) strings of length \(7\) over \(\gf{2}\).
        Hence, apart from isomorphism, the generating matrix and the parity one are the one below.
        \[
            G = \begin{pmatrix}
                0 & 1 & 1 & 1 & 0 & 0 & 0 \\ 
                1 & 1 & 0 & 1 & 1 & 0 & 0 \\ 
                1 & 1 & 0 & 0 & 0 & 1 & 0 \\ 
                1 & 0 & 0 & 1 & 0 & 0 & 1 \\ 
            \end{pmatrix}
            \qquad 
            H = \begin{pmatrix}
                1 & 0 & 0 & 0 & 1 & 1 & 1 \\ 
                0 & 1 & 0 & 1 & 0 & 1 & 1 \\ 
                0 & 0 & 1 & 1 & 1 & 0 & 1
            \end{pmatrix}.
        \]

    \paragraph*{\([3, 1, 3]_{2}\) Hamming code}
    The code is composed of \(2\) strings of length \(3\) over \(\gf{2}\).
        Hence, apart from isomorphism, the generating matrix and the parity one are the one below.
        \[
            G = \begin{pmatrix}
                0 & 0 & 0 \\ 
                1 & 1 & 1 \\
            \end{pmatrix}
            \qquad 
            H = \begin{pmatrix}
                1 & 0 & 1 \\ 
                0 & 1 & 1 \\
            \end{pmatrix}.
        \]

    In addition to being perfect, this code is also optimal as it satisfies the 
        singleton bound.

    \paragraph*{Generalized Hamming codes}
    Consider a field \(\F = \gf{q}, q = p^{m}\). Fix the vector space \(\F^{r}, r \ge 1\). 
    Here, each line vector \(\gen{\bv{w}}\) is a non-empty string \(\bv{w}\) and all it's multiples.
    If we consider the matrix made up by all the \(\bv{w}\), we get a matrix \(H\) with dimension 
    \[
        r \times \frac{q^{r} - 1}{q - 1}.
    \]

    A code \(\C*\) with this \(H\) as parity matrix is called generalized Hamming code, 
        and it's parameter \(n, k, d\) are 
        \[
            n = \frac{q^{r} - 1}{q - 1}, \quad k = \frac{q^{r} - 1}{q - 1} - r, \quad d = 3.
        \]
\end{document}
