\documentclass{subfiles}
\begin{document} 
    Let \(\omega\) be a string to encode, 
    produced by some source \(S\).
    To encode such string we have to:
        \begin{enumerate}
            \item Scan \(\omega\) to get the probabilities of each symbol.
                Unless these are known a priori.
            \item Sort the symbols non-increasingly according to their probabilities.
            \item Build a (binary) tree where the leaves are the source symbols,
                and each node is the sum of the (two) lowest probabilities.
                Repeat the process until a root is formed.
            \item Build the code by traversing the tree from the root to a leaf,
                and assigning a 0 to the left paths, a 1 to the right one.
        \end{enumerate}

        \begin{example*}
            To ease things out, the example skips the scanning step.

            Let \(S = \Set{a, b, c, d, e}\) whose probabilities are
            \(\Set{\tfrac{1}{3}, \tfrac{1}{6}, \tfrac{1}{3},
            \tfrac{1}{12}, \tfrac{1}{12}}\), respectively. 
            Applying the steps above we have the following.
            \begin{description}
                \item [\textbf{Step 1.}] 
                    Sorting the symbols according to the probabilities,
                    we get the following order: \(a, c, b, d, e\).

                \item [\textbf{Step 2.}] 
                    To build the tree let's consider the 
                    two least probable symbols, in this case \(d \text{ and } e\).
                    The sum of their probabilities will define a new node \(x\) in the
                    tree (the \Csquare{rpIris} one in the figures below).
                    The next node \(y\) (the \Csquare{rpFoam} one) is given by \(x\) 
                    and the third least probable symbol \(b\).
                    At this point we can make two choices to define the node \(z\):
                    we can either merge \(a \text{ and } c\) or merge \(c \text{ and } y\).
                    Both will build a optimal code. 
                    
                    For the sake of this example, let's merge \(c \text{ and } y\),
                    the other choice is shown in \emph{Figure \ref{Fig:2.b}}.
                    Lastly, we merge the last two symbols, 
                    leading to the tree in \emph{Figure \ref{Fig:2.a}}.
                    \subfile{../../extra/TikZ/Figure 2 - Example Huffman encoding}

                \item [\textbf{Step 3.}] Traversing the tree we get 
                    \(C = \Set{0, 10, 110, 1110, 1111}\) for tree in 
                    \emph{Figure \ref{Fig:2.a}} or \(C = \Set{00, 01, 10, 110, 111}\)
                    for the one in \emph{Figure \ref{Fig:2.b}}.
            \end{description}   
        \end{example*}

        From the steps above, it's obvious that the slowest part of the encoding
        is given by the neccessity to scan the text twice. 
        Some faster alternatives do exist, and we'll extensively consider one in 
        \emph{Section \ref{Sec:4}}.
\end{document}
